[Artifact57] Robust Resource Bounds with\\ Static Analysis and Bayesian Inference

### 2024-03-11 README/what_is_included.tex
Added a pointer to Appendix C in the paper about automatically choosing hyperparameters

\emph{\textbf{Note:} The tables and plots produced by the artifact are
  slightly different from the ones in the submitted version of the
  paper.
%
  This is because, since the submission, we have adjusted the
  hyperparameters for \BayesWC{} and \BayesPC{} using an automatic
  procedure for choosing hyperparameters.
%
  The updated experiments results still preserve all key findings in
  Section~7 of the paper.
%
  The updated version of the paper accompanies the artifact.}

>>>>

\emph{\textbf{Note:} The tables and plots produced by the artifact are slightly
  different from the ones in the submitted version of the paper.
  %
  This is because, since the submission, we have adjusted the hyperparameters
  for \BayesWC{} and \BayesPC{} using an automatic procedure for choosing
  hyperparameters (Appendix~C of the paper).
  %
  The updated experiments results still preserve all key findings in Section~7
  of the paper.
  %
  The updated version of the paper accompanies the artifact.}
